HPC--101\\Onboarding

### 2023-05-06 hpc_101/sections/01_intro.tex
LTS frame added

>>>>

\begin{frame}
  \frametitle{Permanent Storage }
  \begin{enumerate}
  \item Long Term Storage (LTS)
    \begin{itemize}
    \item {\textbf{Purpose}}: \footnotesize Additional Personal and/or group storage for applications and active data when all other storage options have been exhausted{\mana}\footnote{\label{LTS}\tiny\ \url{https://hawaii.kualibuild.com/app/builder/app/6062a8170d0d97001cb7d3af/run}}

    \end{itemize}
  \end{enumerate}
~\\
  LTS storage on {\mana} has the following attributes:
  \begin{itemize}
  \item \$20/TB with a minimum purchase of 2TB 
  \item LTS purchases are done in a per year basis
  \item Available on all nodes
  \end{itemize}
